### 2016-09-27 architecture.tex
Add missing symbols declaration, fix tests
Consistent non-usage of commas in symbols()
Drop another assumption handler for gamma
We have one example, why second?

For example, consider the expression $xy + 2$:
\begin{verbatim}
>>> expr = x*y + 2
\end{verbatim}
By order of operations, the parent of the expression tree for \texttt{expr} is
an addition, so it is of type \texttt{Add}. The child nodes of \texttt{expr} are
\texttt{2} and \texttt{x*y}.
\begin{verbatim}
>>> type(expr)
<class 'sympy.core.add.Add'>
>>> expr.args
(2, x*y)
\end{verbatim}

@@

As an example of the notions presented in this section,
Listing~\ref{fig:gamma-example} presents a minimal version of the gamma
function $\Gamma(x)$ from SymPy, which evaluates itself on positive integer
arguments, has the positive and real assumptions defined, can be rewritten in
terms of factorial with \verb|gamma(x).rewrite(factorial)|, and can be
differentiated. \texttt{self.func} is used throughout
instead of referencing \texttt{gamma} explicitly so that potential subclasses
of \texttt{gamma} can reuse the methods.

@@

    def _eval_is_positive(self):
        x = self.args[0]
        if x.is_positive:
            return True
        elif x.is_noninteger:
            return floor(x).is_even

>>>>

For example, consider the expression $xy + 2$:
\begin{verbatim}
>>> x, y = symbols('x y')
>>> expr = x*y + 2
\end{verbatim}
By order of operations, the parent of the expression tree for \texttt{expr} is
an addition, so it is of type \texttt{Add}. The child nodes of \texttt{expr} are
\texttt{2} and \texttt{x*y}.
\begin{verbatim}
>>> type(expr)
<class 'sympy.core.add.Add'>
>>> expr.args
(2, x*y)
\end{verbatim}

@@

As an example of the notions presented in this section,
Listing~\ref{fig:gamma-example} presents a minimal version of the gamma
function $\Gamma(x)$ from SymPy, which evaluates itself on positive integer
arguments, has the real assumption defined, can be rewritten in
terms of factorial with \verb|gamma(x).rewrite(factorial)|, and can be
differentiated. \texttt{self.func} is used throughout
instead of referencing \texttt{gamma} explicitly so that potential subclasses
of \texttt{gamma} can reuse the methods.

@@
